Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View

### 2020-07-22 Manuscript/sec2-review-of-graph-neural-network.tex
update GaAN

Different GNNs adopt different kinds of graph neurons and have different definitions of the three functions.
$\phi$ and $\Sigma$ are the \emph{edge calculation} functions.
They are conducted over every edge in $\mathcal{G}$.
$\gamma$ is the \emph{vertex calculation} function.
It is conducted over every vertex in $\mathcal{G}$.
\tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} list the edge functions and the vertex functions of typical GNNs, respectively.
For ChebNet, we report its GNN sub-layer in the tables. 
A ChebNet layer consists of $K$ GNN sub-layers and a summation layer:
$\boldsymbol{H}^{l+1} = \sum_{k=1}^K{\boldsymbol{Z}^{(k)} \textcolor{blue}{\boldsymbol{W}^{(k)}}}$ with the GNN sub-layers $\boldsymbol{Z}^{(1)}=\boldsymbol{H}^l$, $\boldsymbol{Z}^{(2)}=\hat{\boldsymbol{L}}\boldsymbol{H}^l$, and $\boldsymbol{Z}^{(k)}=2\hat{\boldsymbol{L}}\boldsymbol{Z}^{(k-1)} - \boldsymbol{Z}^{(k-2)}$, where $\boldsymbol{H}^l$ is the matrix of output hidden feature vectors of the layer $l-1$.
For GAT, a GAT layer consists of two sub-layers and it conducts part of the vertex calculation before the two sub-layers.
For GaAN, a GaAN layer consists of four sub-layers: the first sub-layer calculates the summation $\boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp(\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l) \odot \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l))$, and the other three layers calculate $\boldsymbol{m}^l_{j,i,1}$/$\boldsymbol{m}^l_{j,i,2}$/$\boldsymbol{m}^l_{j,i,3}$.

@@

						 & \boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp(\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l) \odot \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l)) \\

@@

						 & \alpha^l_{j, i, (k)} = \frac {\exp(\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l) \odot \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l))} {\hat{\boldsymbol{a}}^{l, 0}_{i, (k)}}\\
						 & \boldsymbol{m}_{j, i}^{l, 1} = \parallel_{k=1}^K \alpha_{j, i, (k)} \textcolor{blue}{\boldsymbol{FC}^h_{\theta^l_v}} \hat{\boldsymbol{h}}_{j, (k)}^l \\                                                                                                                                                                                                                                                                                           

@@

						 & \boldsymbol{m}_{j, i}^{l, 2} = \textcolor{blue}{\boldsymbol{FC}_{\theta^l_m}} \boldsymbol{h}_j^{l}  \\

@@

		Blue variables are model parameters to learn. In GaAN, $FC^{\alpha}_{\theta}(x) = \alpha(\boldsymbol{W}\boldsymbol{x} + \boldsymbol{b})$, 
		where $\theta=\{\boldsymbol{W}, \boldsymbol{b}\}$, $\theta$ with different subscripts mean different transformation parameters, we denote $h(\cdot)$
		to be the $LeakyReLU$ for activation functions and $FC_{\theta}(x)$ means applying no activation function after the linear transform.

@@

						& \text{Sub-layer 1,2,3:}\\
						& \boldsymbol{g}_i^l = \textcolor{blue}{\boldsymbol{FC}_{\theta^l_g}}(\boldsymbol{h}_i^{l} \parallel \boldsymbol{s}_{i}^{l, 2} \parallel \boldsymbol{s}_{i}^{l, 3}) \\
						& \boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{FC}_{\theta^l_o}} (\boldsymbol{h}_i^l \parallel (\boldsymbol{g}_{i}^l \odot \boldsymbol{s}_{i}^{l, 1}))

@@

		In GaAN, $FC^{\alpha}_{\theta}(x) = \alpha(\boldsymbol{W}\boldsymbol{x} + \boldsymbol{b})$, 
		where $\theta=\{\boldsymbol{W}, \boldsymbol{b}\}$, $\theta$ with different subscripts mean different transformation parameters, we denote $h(\cdot)$
		to be the $LeakyReLU$ for activation functions and $FC_{\theta}(x)$ means applying no activation function after the linear transform.}

>>>>

Different GNNs adopt different kinds of graph neurons and have different definitions of the three functions.
$\phi$ and $\Sigma$ are the \emph{edge calculation} functions.
They are conducted over every edge in $\mathcal{G}$.
$\gamma$ is the \emph{vertex calculation} function.
It is conducted over every vertex in $\mathcal{G}$.
\tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} list the edge functions and the vertex functions of typical GNNs, respectively.
For ChebNet, we report its GNN sub-layer in the tables. 
A ChebNet layer consists of $K$ GNN sub-layers and a summation layer:
$\boldsymbol{H}^{l+1} = \sum_{k=1}^K{\boldsymbol{Z}^{(k)} \textcolor{blue}{\boldsymbol{W}^{(k)}}}$ with the GNN sub-layers $\boldsymbol{Z}^{(1)}=\boldsymbol{H}^l$, $\boldsymbol{Z}^{(2)}=\hat{\boldsymbol{L}}\boldsymbol{H}^l$, and $\boldsymbol{Z}^{(k)}=2\hat{\boldsymbol{L}}\boldsymbol{Z}^{(k-1)} - \boldsymbol{Z}^{(k-2)}$, where $\boldsymbol{H}^l$ is the matrix of output hidden feature vectors of the layer $l-1$.
For GAT, a GAT layer consists of two sub-layers and it conducts part of the vertex calculation before the two sub-layers.
For GaAN, a GaAN layer consists of four sub-layers: the first sub-layer calculates the summation $\boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp((\textcolor{blue}{W^{l, k}_{xa}} \boldsymbol{h}_j^l + \textcolor{blue}{b^{l, k}_{xa}})^T (\textcolor{blue}{\boldsymbol{W}^{l, k}_{ya}} \boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{b}^{l,k}_{ya}}))$, and the other three layers calculate $\boldsymbol{m}^l_{j,i,1}$/$\boldsymbol{m}^l_{j,i,2}$/$\boldsymbol{m}^l_{j,i,3}$.

@@

						 & \boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp((\textcolor{blue}{W^{l, k}_{xa}} \boldsymbol{h}_j^l + \textcolor{blue}{b^{l, k}_{xa}})^T (\textcolor{blue}{\boldsymbol{W}^{l, k}_{ya}} \boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{b}^{l,k}_{ya}})) \\

@@

						 & \alpha^l_{j, i, (k)} = \frac {\exp((\textcolor{blue}{W^{l, k}_{xa}} \boldsymbol{h}_j^l + \textcolor{blue}{b^{l, k}_{xa}})^T (\textcolor{blue}{\boldsymbol{W}^{l, k}_{ya}} \boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{b}^{l,k}_{ya}}))} {\hat{\boldsymbol{a}}^{l, 0}_{i, (k)}}\\
						 & \boldsymbol{m}_{j, i}^{l, 1} = \parallel_{k=1}^K \alpha_{j, i, (k)} LeakyReLU(\textcolor{blue}{\boldsymbol{W}^{l, k}_v} \boldsymbol{h}_j^l + \textcolor{blue}{b^{l, k}_v}) \\                                                                                                                                                                                                                                                                                           

@@

						 & \boldsymbol{m}_{j, i}^{l, 2} = \textcolor{blue}{\boldsymbol{W}^l_m} \boldsymbol{h}_j^{l} + \textcolor{blue}{\boldsymbol{b}^l_m} \\

@@

@@

						& \boldsymbol{g}_i^l = \textcolor{blue}{\boldsymbol{W}^l_g}[\boldsymbol{h}_i^{l} \parallel \boldsymbol{s}_{i}^{l, 2} \parallel \boldsymbol{s}_{i}^{l, 3}] + \textcolor{blue}{\boldsymbol{b}^l_g} \\
						& \boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{W}^l_o} [\boldsymbol{h}_i^l \parallel (\boldsymbol{g}_{i}^l \odot \boldsymbol{s}_{i}^{l, 1})] + \textcolor{blue}{\boldsymbol{b}^l_o}

@@
